The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-18 article.tex
Cleaned up the 'code maintenance' intro section (closes #39)

As the library grew over the years, so did the maintenance become more complex. Increasingly,
the main branch did not compile, and bug fixing become increasingly difficult, as fixing a bug
in one part of the code, broke some other code which made the wrong assumption about the first
code.

To address these issues, we have adopted a number of coding standards. By no means there are
meant to implement the best practices of source code development; instead, they attempt to find
a balance between increasing code maintainability and being flexible enough to allow efficient
code development. However, we appreciate the subjective nature of this statement, and some
adopted guidelines have been heavily discussed in the community.
The next sections describe some approaches the project have adopted that allows us to
maintain the CDK library as it is today.

However, perhaps the biggest factor in improved code quality is that we
instantiated a peer review process where any functionality changing patch is
required to be reviewed by one independent, senior CDK developer for  the development
branch, and two reviewers for stable branches. This patch development system
is supported by a number of automated validations steps as outlined below.

>>>>

As the library grew over the years, so did the complexity of the maintenance:
Increasingly frequent, the main branch faied to compile, and bug fixing become
more difficult with unexpected side effects. Often fixing a bug in one part of
the code, broke some other code which made the incorrect assumptions about the
fixed code. Such is inevitable when the number of developers increases.

To address these issues, we have adopted a number of coding standards. By no
means these are meant to implement the best practices of source code development,
which is not practically unfeasible with limited resources; instead, they attempt
to find a balance between increasing code maintainability and being flexible
enough to allow efficient code development. However, we appreciate the subjective 
nature of this statement, and some adopted guidelines have been heavily discussed
and debated in the CDK community.

Arguably, perhaps the biggest factor in improved code quality is that we
instantiated a peer review process where any functionality changing patch is
required to be reviewed by one independent, senior CDK developer for the development
branch, and two reviewers for stable branches. This patch development system
is supported by a number of automated validations steps as outlined below.

The next sections describe some approaches the project have adopted that allows
us to maintain the CDK library as it is today.
